%(online selection, skims, yields)
%\subsection{Minimum bias}
\chapter{Datasets}
\subsection{PbPb dimuon trigger and skim}

A primary dataset (/HIDiMuon/HIRun2011-PromptReco-v1/RECO) based on
all events selected by the muon trigger has been used for this
analysis. The RAW files and the prompt reconstruction files are stored
at T1\_FR\_CCIN2P3. At the Tier-1, they were skimmed for events with
two global muons that form a pair with an invariant mass of more than
2\GeVcc (/HIDiMuon/\\tdahms-Onia2MuMu\_Skim-v3-*/USER). All charge
combinations have been considered in the pairing. In addition to a
muon trigger firing in the event a coincidence with the minimum bias
trigger was required. This minimum bias trigger was defined by the
logical or of the following three triggers, which were unprescaled during the run:
\begin{itemize}
\item A bunch crossing signal sent by the BPTX (BptxAND) and,  two coincident HF
towers above a certain threshold (set in the firmware) on each side of the detector (HcalHfCoincPm) or at least one BSC segment (of the 16) giving a signal on each side of the detector (BscMinBiasThreshold 1):\\
  L1\_HcalHfCoincPmORBscMinBiasThresh1\_BptxAND\_instance1.
\item BSCThreshold1 which requires at least one BSC hit on each side (out of the 32 channels): 'L1\_NotBsc2\_BscMinBiasOR. `NotBsc2' is always 'True' so it can be ignored.
\item coincidence of two HF towers on each side of the detector: HFL1\_HcalHfCoincidencePm.
\end{itemize}

Signal candidates are required to have fired the trigger path  {{HLT\_HIL1DoubleMu0\_HighQ}}. This trigger was unprescaled during the whole run. It is based solely on L1 decisions and requires the
presence of two L1 muon objects with quality $>4$, without any
constraint on their momenta. Coincidence with the BPTX trigger is required. 
The trigger path has tighter quality requirements than the path HLT\_HIL1DoubleMuOpen  
used in the 2010 \PbPb run, and than the path 
HLT\_L1DoubleMu0 used in the 2011 \pp 2.76TeV run. 

Furthermore, the default good event selection as in the 2010 analysis
has been applied. This requires a veto on BSC halo triggers, a
reconstructed primary vertex with two or more tracks, and the pixel
cluster-length being compatible with the primary vertex to reject PKAM
events. An additional requirement to remove UPC (ultra-peripheral collisions) events was the offline
HF coincidence, requiring at least 3 HF towers on each side of the
interaction point with at least 3\GeV energy deposited per tower.

In summary, the events used for this analysis are required to pass the
following filters : the BSC halo filter, a reconstructed primary
vertex made of at least two tracks, the pixel cluster-length
compatibility with the vertex, the requirement of an off-line HF
coincidence with at least 3 towers on each side of the interaction
point in the HF with at least 3 GeV energy deposited per tower, and the  {{HLT\_HIL1DoubleMu0\_HighQ}} muon trigger.

The CMSSW release 4\_4\_2\_patch5 and the global tag GR\_P\_V27A were
used during the skimming and analysis steps.

\subsection{pp sample}

The same \pp sample as for the 2010 analysis has been used~\cite{CMS_PAS_HIN-10-006,prl,QM2011}. 
Signal candidates are required to have fired the trigger path HLT\_L1DoubleMu0.
%{{HLT\_HIL1DoubleMuOpen}} => this pone was used for pbpb data in 2010
%
The data have been re-reconstructed in the same CMSSW release as the 2011 \PbPb
data (4\_4\_2\_patch5) with the global tag GR\_R\_44\_V10:
/AllPhysics2760/Nov2011\_HI-SD\_MuHI-276TeV\_ppRereco/RECO.

%summary of path names:
%PbPb (old MC): HLT_HIL1DoubleMuOpen_v1
%PbPb (new MC): HLT_HIL1DoubleMu0_HighQ_v1
%pp (old MC): HLT_L1DoubleMu0_v1
%pp (newd MC): HLT_HIL1DoubleMu0_HighQ_v1


\subsection{Monte Carlo samples}

\PgUa events were simulated in \PYTHIA and embedded into
\textsc{hydjet} as for last year's analysis. For this \PgUa were
generated with realistic \pt and rapidity distributions in several
bins of \pt (0--3, 3--6, 6--9, 9--12, 12--15, 15--30, and $>30\GeVc$)
to enhance the statistics at high \pt:\\
/Hydjet\_Bass\_MinBias\_2760GeV/davidlw-PyquenEvtGen\_upsilon1sMuMu\_upsPt*-Summer11-STARTHI44\_V7-v1-GEN-SIM-RECO\_v3-58956c214fa8e92cbba029d2c88707a9/USER

\end{chapter}
